Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-06-06 paper_jasa.tex
small updates

\begin{table}[htp]
\caption{Possible $p$-values for different numbers of observers, $K$, for fixed size $m = 20$ lineups.}
\begin{center}
\begin{tabular}{|rrr|rrr|rrr|rrr|rrr|}\hline
$K$ &  $x$ & $p$-value & $K$ &  $x$ & $p$-value & $K$ &  $x$ & $p$-value & $K$  & $x$ & $p$-value & $K$  & $x$ & $p$-value\\\hline
1 &  1 & 0.0500 & 2 &  1 & 0.0975 & 3 & 1 & 0.1426 & 4 & 1 & 0.1855 & 5 & 1 & 0.2262 \\%\cline{1-3}
&&& 2 &  2 & 0.0025 & 3 & 2 & 0.0073 & 4 & 2 & 0.0140 & 5 & 2 & 0.0226 \\
&&& &&& 3 & 3 & 0.0001 & 4 & 3 & 0.0005 & 5 & 3 & 0.0012 \\%\cline{1-6}
&&&  &    &        &   &   &        & 4 & 4 & $< 0.0001$ & 5 & 4 & $< 0.0001$ \\\hline
\end{tabular}
\end{center}
\label{pvalue}
\end{table}

>>>>

\begin{table}[htp]
\caption{Possible $p$-values for different numbers of observers, $K$, for fixed size $m = 20$ lineups.}
\begin{center}
\begin{tabular}{rrrrrrrrrrrrrrrrrrr}
$K$ &  $x$ & $p$-value && $K$ &  $x$ & $p$-value && $K$ &  $x$ & $p$-value && $K$  & $x$ & $p$-value && $K$  & $x$ & $p$-value\\ \cline{1-3} \cline{5-7}\cline{9-11}\cline{13-15}\cline{17-19}
1 &  1 & 0.0500 && 2 &  1 & 0.0975 && 3 & 1 & 0.1426 && 4 & 1 & 0.1855 && 5 & 1 & 0.2262 \\%\cline{1-3}
&&&& 2 &  2 & 0.0025 && 3 & 2 & 0.0073 && 4 & 2 & 0.0140 && 5 & 2 & 0.0226 \\
&&&& &&&& 3 & 3 & 0.0001 && 4 & 3 & 0.0005 && 5 & 3 & 0.0012 \\%\cline{1-6}
&&&&  &    &        &   &   &        &&& 4 & 4 & $< 0.0001$ && 5 & 4 & $< 0.0001$ 
\end{tabular}
\end{center}
\label{pvalue}
\end{table}
